Notes on the low density parameters in {\tt MAESTRO}

### 2009-02-06 docs/lo_density/lo_density.tex
updated the base cutoff density section

@@

\item In {\tt make\_hgrhs}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt anelastic\_cutoff\_coord}-1]$.

\item In {\tt make\_macrhs}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt anelastic\_cutoff\_coord}-1]$.

@@

\item In {\tt make\_grav}, if we are spherical, we do not add to the
  enclosed mass, $M(r)$ if $\rho$ is less than {\tt base\_cutoff\_density}.
\end{itemize}

>>>>

\item In {\tt probin}, {\tt base\_cutoff\_density} is set to $3\times 10^6$
  by default.

@@

\item In {\tt make\_hgrhs}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt make\_macrhs}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

\item In {\tt make\_w0}, we only add the volume discrepancy for
  $r\in[{\tt r\_start\_coord},{\tt base\_cutoff\_density\_coord}-1]$.

@@

\item In {\tt make\_grav}, if we are spherical, we do not add to the
  enclosed mass, $M(r)$ if $\rho$ is less than {\tt base\_cutoff\_density}.

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r\in[{\tt base\_cutoff\_density\_coord}-1]$
